---
title       : Fuel Economy Information
subtitle    : 
author      : Venkat Vasam
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview

1. Summary of the data set variables
2. Fuel economy based on number of Cylinders
3. Fuel economy based on type of Transmission
4. Fuel economy based on engine's diplacement in liters
5. Fuel economy based on class(Type) of car
6. Questions and Answers


--- .class #id 

## Summary of the data set variables


```{r  echo = FALSE, include=TRUE,cache=TRUE,warning=FALSE,message=FALSE,comment=NA }

library(ggplot2)

summary(mpg)

```


--- .class #id 

## Fuel economy based on number of Cylinders


```{r  echo = FALSE, include=TRUE,cache=TRUE,warning=FALSE,message=FALSE,comment=NA }

xTitle<-'Number of Cylinderss'

xVar<-"cyl"
yVarH<-"Highway"
yVarC<-"City"

mpginshwy<-data.frame(mpg[,xVar],mpg$hwy)

colnames(mpginshwy) <- c(xVar, yVarH)

mpginscty<-data.frame(mpg[,xVar],mpg$cty)

colnames(mpginscty) <- c(xVar, yVarC)

plotinshwy<-ggplot(mpginshwy, aes_(x=as.name(xVar), y=as.name(yVarH),color=as.name(yVarH) ))+geom_boxplot()


plotinscty<-ggplot(mpginscty, aes_(x=as.name(xVar), y=as.name(yVarC),color=as.name(yVarC) ))+geom_boxplot()

grid.arrange(plotinshwy,plotinscty)

```

--- .class #id 

## Fuel economy based on type of Transmission


```{r  echo = FALSE, include=TRUE,cache=TRUE,warning=FALSE,message=FALSE,comment=NA }

xTitle<-'Type of Transmission'

xVar<-"trans"
yVarH<-"Highway"
yVarC<-"City"

mpginshwy<-data.frame(mpg[,xVar],mpg$hwy)

colnames(mpginshwy) <- c(xVar, yVarH)

mpginscty<-data.frame(mpg[,xVar],mpg$cty)

colnames(mpginscty) <- c(xVar, yVarC)

plotinshwy<-ggplot(mpginshwy, aes_(x=as.name(xVar), y=as.name(yVarH),color=as.name(yVarH) ))+geom_boxplot()


plotinscty<-ggplot(mpginscty, aes_(x=as.name(xVar), y=as.name(yVarC),color=as.name(yVarC) ))+geom_boxplot()

grid.arrange(plotinshwy,plotinscty)

```

--- .class #id 

## Fuel economy based on engine's diplacement in liters


```{r  echo = FALSE, include=TRUE,cache=TRUE,warning=FALSE,message=FALSE,comment=NA }

xTitle<-'Engine Displacement in Liters'

xVar<-"displ"
yVarH<-"Highway"
yVarC<-"City"

mpginshwy<-data.frame(mpg[,xVar],mpg$hwy)

colnames(mpginshwy) <- c(xVar, yVarH)

mpginscty<-data.frame(mpg[,xVar],mpg$cty)

colnames(mpginscty) <- c(xVar, yVarC)

plotinshwy<-ggplot(mpginshwy, aes_(x=as.name(xVar), y=as.name(yVarH),color=as.name(yVarH) ))+geom_boxplot()


plotinscty<-ggplot(mpginscty, aes_(x=as.name(xVar), y=as.name(yVarC),color=as.name(yVarC) ))+geom_boxplot()

grid.arrange(plotinshwy,plotinscty)

```

--- .class #id 

## Fuel economy based on class(Type) of car


```{r  echo = FALSE, include=TRUE,cache=TRUE,warning=FALSE,message=FALSE,comment=NA }

xTitle<-'Class ( Type) of car'

xVar<-"class"
yVarH<-"Highway"
yVarC<-"City"

mpginshwy<-data.frame(mpg[,xVar],mpg$hwy)

colnames(mpginshwy) <- c(xVar, yVarH)

mpginscty<-data.frame(mpg[,xVar],mpg$cty)

colnames(mpginscty) <- c(xVar, yVarC)

plotinshwy<-ggplot(mpginshwy, aes_(x=as.name(xVar), y=as.name(yVarH),color=as.name(yVarH) ))+geom_boxplot()


plotinscty<-ggplot(mpginscty, aes_(x=as.name(xVar), y=as.name(yVarC),color=as.name(yVarC) ))+geom_boxplot()

grid.arrange(plotinshwy,plotinscty)

```

--- .class #id 

## Questions and Answers

--- .class #id 
