---
title       : Fuel Economy Information
subtitle    : 
author      : Venkat Vasam
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview

1. Summary of the data set variables
2. R Code To Show Box Plot of Fuel economy based on number of Cylinders
3. Sample Box Plot View of App for Fuel economy based on number of Cylinders
4. Shiny App URL: https://vvasam.shinyapps.io/ddshinyapp/
5. Github repository: https://github.com/vvasamgit/ddp4


--- .class #id 

## Summary of the data set variables

```{r  echo = FALSE, include=TRUE,cache=TRUE,warning=FALSE,message=FALSE,comment=NA }

library(ggplot2)
summary(mpg)
```

--- .class #id 


##  R Code To Show Box Plot of Fuel economy based on number of Cylinders


```{r  echo = TRUE, include=TRUE,eval=FALSE,cache=TRUE,warning=FALSE,message=FALSE,comment=NA }

library(ggplot2)
library(dplyr)
library(gridExtra)
xTitle<-'Number of Cylinderss'
xVar<-"cyl"
yVarH<-"Highway"
yVarC<-"City"
mpginshwy<-data.frame(mpg[,xVar],mpg$hwy)
colnames(mpginshwy) <- c(xVar, yVarH)
mpginscty<-data.frame(mpg[,xVar],mpg$cty)
colnames(mpginscty) <- c(xVar, yVarC)
plotinshwy<-ggplot(mpginshwy, aes_(x=as.name(xVar), y=as.name(yVarH),color=as.name(yVarH) ))
+geom_boxplot()
plotinscty<-ggplot(mpginscty, aes_(x=as.name(xVar), y=as.name(yVarC),color=as.name(yVarC) ))
+geom_boxplot()
grid.arrange(plotinshwy,plotinscty)

```

--- .class #id 

## Sample Box Plot View of App for Fuel economy based on number of Cylinders

```{r  echo = FALSE, include=TRUE,cache=TRUE,warning=FALSE,message=FALSE,comment=NA }

library(ggplot2)
library(dplyr)
library(gridExtra)

xTitle<-'Number of Cylinderss'

xVar<-"cyl"
yVarH<-"Highway"
yVarC<-"City"

mpginshwy<-data.frame(mpg[,xVar],mpg$hwy)

colnames(mpginshwy) <- c(xVar, yVarH)

mpginscty<-data.frame(mpg[,xVar],mpg$cty)

colnames(mpginscty) <- c(xVar, yVarC)

plotinshwy<-ggplot(mpginshwy, aes_(x=as.name(xVar), y=as.name(yVarH),color=as.name(yVarH) ))+geom_boxplot()


plotinscty<-ggplot(mpginscty, aes_(x=as.name(xVar), y=as.name(yVarC),color=as.name(yVarC) ))+geom_boxplot()

grid.arrange(plotinshwy,plotinscty)

```
